Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
minoe

Table~\ref{tbl:corpus-type-breakdown} reports on the 10 most frequent types
occuring in the corpus. Scalar doubles account for 11\% function arguments,
whereas logicals represent 27\% of observed values.  Together, \lgl and \chr
account for 60\%.

\begin{table}[!h]
% BEGIN Autogenerated
\small
\begin{tabular}{lrrrr}
\toprule
Type & Args & \% of Args & Observations & \% of Observations\\
\midrule
\dbl & 13,255 & 11.06 & 41,560,797 & 1.59\\
\lgl & 10,142 & 8.46 & 712,895,959 & 27.21\\
\null & 9,175 & 7.66 & 122,202,183 & 4.66\\
\chr & 9,171 & 7.65 & 794,058,588 & 30.31\\
\VEC\dbl & 7,811 & 6.52 & 29,272,232 & 1.12\\
\addlinespace
\VARGS & 7,759 & 6.48 & 76,369,333 & 2.92\\
\any & 6,243 & 5.21 & 255,539,497 & 9.75\\
\VEC\chr & 4,576 & 3.82 & 88,233,523 & 3.37\\
\CLASS{matrix} & 4,522 & 3.77 & 32,452,555 & 1.24\\
\CLASS{data.frame} & 2,781 & 2.32 & 7,749,094 & 0.30\\
\bottomrule
\end{tabular}

% END Autogenerated
\label{tbl:corpus-type-breakdown}
\caption{Top types of arguments in R.}
\end{table}

>>>>

Table~\ref{ctb} reports on the 10 most frequent types
occuring in the corpus. Scalar doubles account for 11\% function arguments,
whereas logicals represent 27\% of observed values.  Together, \lgl and \chr
account for 60\%.

\begin{table}[!h]
% BEGIN Autogenerated
\small
\begin{tabular}{lrrrr}
\toprule
Type & Args & \% of Args & Observations & \% of Obs.\\
\midrule
\dbl & 13,255 &     11.0 & 41,560,797 & 1.5\\
\lgl & 10,142 &      8.4 & 712,895,959 & 27.2\\
\null & 9,175 &      7.6 & 122,202,183 & 4.6\\
\chr & 9,171 &       7.5 & 794,058,588 & 30.3\\
\VEC\dbl & 7,811 &   6.5 & 29,272,232 & 1.1\\
\VARGS & 7,759 &     6.4 & 76,369,333 & 2.9\\
\any & 6,243 &       5.2 & 255,539,497 & 9.0\\
\VEC\chr & 4,576 &   3.8 & 88,233,523 & 3.3\\
\CLASS{matrix} & 4,522     & 3.7 & 32,452,555 & 1.2\\
\CLASS{data.frame} & 2,781 & 2.3 & 7,749,094 & 0.3\\
\bottomrule
\end{tabular}

% END Autogenerated
\caption{Top types of arguments in R}\label{ctb}
\end{table}
